Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system of plausible mechanism

### 2024-08-16 _tex/index.tex
Built site for gh-pages

The structural approach, however, offers a notable advantage over the
potential outcomes approach by allowing the graphical and formal
representation of theories through directed acyclic graphs
\citep[DAG,][]{Pearl_2009, Pearl_et_al_2016, Gross_et_al_2018, Neal_2020}.
DAGs function as heuristics, effectively conveying the presumed causal
structure of a system, referred to as a \emph{scientific model}
\citep{McElreath_2020}. They do not represent detailed statistical
models but allow researchers to deduce which statistical models can
provide valid causal inferences, assuming the causal structure depicted
in the DAGs are accurate \citep{McElreath_2020}. The
Identification-Estimation flowchart in Figure~\ref{fig-IEflow} visually
represents this process of transitioning from estimands to estimates, as
well as the application of the scientific model and data to identify and
estimate causal effects.

>>>>

The structural approach, however, offers a notable advantage over the
potential outcomes approach by allowing the graphical and formal
representation of theories through directed acyclic graphs
\citep[DAG,][]{Pearl_2009, Pearl_et_al_2016, Gross_et_al_2018, Neal_2020}.
DAGs function as heuristics, effectively conveying the presumed causal
structure of a system, referred to as a \emph{scientific model}. They do
not represent detailed statistical models but allow researchers to
deduce which statistical models can provide valid causal inferences,
assuming the causal structure depicted in the DAGs are accurate
\citep{McElreath_2020}. The Identification-Estimation flowchart in
Figure~\ref{fig-IEflow} visually represents this process of
transitioning from estimands to estimates, as well as the application of
the scientific model and data to identify and estimate causal effects.
